Data Analysis Project

### 2024-07-28 products/manuscript/Manuscript.qmd
commit changes

Observation: There are several outliers with BMI values above 50, indicating that there are individuals with unusually high BMI compared to the rest of the dataset.\@fig-outliers-charges shows the outliers in charges

@@

*Include citations in your Rmd file using bibtex, the list of references will automatically be placed at the end*

This paper [@leek2015] discusses types of analyses.

These papers [@mckay2020; @mckay2020a] are good examples of papers published using a fully reproducible setup similar to the one shown in this template.

Note that this cited reference will show up at the end of the document, the reference formatting is determined by the CSL file specified in the YAML header. Many more style files for almost any journal [are available](https://www.zotero.org/styles). You also specify the location of your bibtex reference file in the YAML. You can call your reference file anything you like.

>>>>

Observation: There are several outliers with BMI values above 50, indicating that there are individuals with unusually high BMI compared to the rest of the dataset.\@fig-outliers-charges shows the outliers in charges.

@fig-outliers-charges shows the outliers in Charges

@@

This website [@careinsurance_smoker] discusses the challenges smokers face in obtaining health insurance, highlighting how smoking affects premium costs..

This Experian website [@experian_premium_factors] explains various factors that affect health insurance premium costs, including age, location, tobacco use, type of plan, and individual vs. family enrollment. It provides insights on how these factors influence the overall cost of health insurance for consumers..

The article [@choi_blackburn_2018] examines how household sociodemographic characteristics influence health insurance premiums and medical expenses. Using data from the 2014 Consumer Expenditure Survey, the study identifies that age, marital status, educational attainment, and family income are significant predictors of higher spending on health insurance premiums and medical expenses. .
